### 2019-04-25 manuscript/response.tex

\begin{quote}
--115 I'm uncomfortable with this way of handling multiple cytotypes.
The most commonly reported cytotype could easily not be the most common cytotype in the wild (I assume that most taxa are represented by relatively few counts), and regardless, there is biology here.
Specifically, this methodology would artificially reduce the number of ploidy changes (if a taxon is polymorphic for ploidy, there's at least one event there), and the omitted changes would be disproportionately those towards the tips of the phylogeny, so not only would rates be depressed, but the bias is of a sort that the estimation of diversification parameters is particularly sensitive to (the authors will understand why this is so).
\end{quote}

Rosana? % TODO

\begin{quote}
--130 I don't follow this discussion.
There's a self-incompatible pentaploid?
How is it even sexual?
Regardless, the discussion of this pentaploid should be more clearly integrated back into the central argument here, about the absense of SI polyploids (I think that's the central argument?).
\end{quote}

Maybe skip more quickly over this weird case, if it is more of a distraction than an explanation?
We could also maybe revise the following sentences once we have more explanation of no-SI-P in the Intro.
Boris? % TODO

@@

\begin{quote}
--the use of run time as a description of the analysis seems odd to me.
As a reader, I'm not interested in the power of a given computer -- I want to know how many generations the MCMC was run for, what the ESSs are, etc.
\end{quote}

Seems reasonable.  Rosana? % TODO

\begin{quote}
-325  These analyses (by accounting for diversification) may take care of this issue, but is there a problem with these results being driven by a non-stationary process being modeled as a stationary one?
\end{quote}

This was a point worth considering, but our model does not assume stationarity.
In Fig.~4, the contributions of each pathway are functions of time.
We can see there both the short-term and long-term behavior.
% Rosana, what do you think?

### 2019-04-25 manuscript/introduction.tex
more reviewer responses
mostly Methods and Results
including revised text to explain the pathway findings

Given that changes in ploidy and breeding systems are causally related, and may have profound effects on the fate of lineages, it seems particularly profitable to examine possible interactions in their macroevolutionary effects.
If the effects of ploidy and breeding system on lineage diversification are not additive, studying each trait separately may not reveal the effects of their combinations.
As a result, it may be of interest to establish their joint influence on speciation and extinction rates.
The two traits may also affect each other's state transitions.
For example, losses of SI in diploids could be caused by polyploidization, resulting in a one-step pathway to polyploid SC species. 
Alternatively, the path from SI diploids to SC polyploids may involve a transition to SC, without an increase in ploidy, and then a subsequent polyploidization. 
\citet{robertson_2011} found that the pathway from SI diploids to SC polyploids is dominated by the two-step pathway over long timescales, but generally proceeds in one step via polyploidization of SI species over short timescales.
It remains to be seen whether these results hold true when allowing for the influence of these traits on lineage diversification.

>>>>

Given that changes in ploidy and breeding systems are causally related, and may have profound effects on the fate of lineages, it seems particularly profitable to examine possible interactions in their macroevolutionary effects.
If the effects of ploidy and breeding system on lineage diversification are not additive, studying each trait separately may not reveal the effects of their combinations.
As a result, it may be of interest to establish their joint influence on speciation and extinction rates.
The two traits may also affect each other's state transitions.
For example, losses of SI in diploids could be caused by polyploidization, resulting in a one-step pathway to polyploid SC species. 
Alternatively, the path from SI diploids to SC polyploids may involve a transition to SC, without an increase in ploidy, and then a subsequent polyploidization. 
\citet{robertson_2011} compared the contributions of these two paths, finding that evolution from SI diploid to SC polyploid is more likely to proceed via the one-step pathway over short timescales, but via the two-step pathway over long timescales.
Their analysis considered only transitions among the states, however, so it remains to be seen whether these results hold true when allowing for the influence of these traits on lineage diversification.

### 2019-04-25 manuscript/results.tex
more reviewer responses
mostly Methods and Results
including revised text to explain the pathway findings

There are two pathways by which SI diploid lineages eventually---given enough time---become a SC polyploid.
In the one-step pathway, polyploidization directly disables SI.
In the two-step pathway, SI is first lost within the diploid state, followed by polyploidization.
Determining the relative contribution of these pathways based on our estimated transition rates from the ID/CD/CP model, we find that the one-step pathway is more likely on short timescales and the two-step pathway is more likely on long timescales (\cref{figure:pathways}, left panels).
Beginning with a single SI diploid (ID) lineage, when not much time has elapsed, the one-step pathway is more likely because it only necessitates a single event to effect transition to SC polyploid state.
When more time has elapsed, the two-step pathway is more likely because the rate of loss of SI within diploids, $q_{IC}$, is greater than the rate of polyploidization for SI species, $\rho_I$ (\cref{suppfigure:IDCDCPnodip}).
These conclusions, however, ignore the changes in numbers of lineages in a particular state from speciation and extinction events.
By analogy, frequent sinking of a middle stepping stone in a path would lower the value of such a path.
We therefore examined the effects of diversification rate on relative importance of each pathway.
%B: revisit this possibly terrible analogy.

Indeed, incorporation of lineage diversification rates changes conclusions regarding the relative contribution of each pathway.
Beginning with a single ID lineage, assessment of relative pathway importance necessitates consideration of proliferation in the ID state, as well as the CD state for the two-step pathway, and to track the transitions to the CP state.
In this situation, even over long timescales, the two-step pathway contributes less to generation of CP (\cref{figure:pathways}, right panels).
The lower rate of net diversification in the CD state, relative to ID, means that relatively fewer lineages are available to complete the second step of the two-step pathway, ending in CP.

>>>>

There are two pathways by which SI diploid lineages eventually---given enough time---become SC polyploids.
In the one-step pathway, polyploidization directly disables SI.
In the two-step pathway, SI is first lost within the diploid state, followed by polyploidization.
Determining the relative contribution of these pathways based on our estimated transition rates from the ID/CD/CP model, we find that the one-step pathway is more likely on short timescales and the two-step pathway is more likely on long timescales (\cref{figure:pathways}, left panels).
Beginning with a single SI diploid lineage, when not much time has elapsed, the one-step pathway is more likely because it only necessitates a single event to effect transition to SC polyploid state.
When more time has elapsed, the two-step pathway is more likely because the rate of loss of SI within diploids, $q_{IC}$, is greater than the rate of polyploidization for SI species, $\rho_I$ (\cref{suppfigure:IDCDCPnodip}).

The preceding conclusions, however, ignore the changes in numbers of lineages in each state due to speciation and extinction.
By analogy, envisioning the states as stepping stones, the extent to which each stone grows or shrinks over time affects the utility of each possible path.
Allowing for the different net diversification rates for each state, we find a qualitative difference in the relative pathway contributions.
In particular, the lower rate of net diversification in the CD state, relative to ID, means that relatively fewer lineages are available to complete the second step of the two-step pathway, ending in CP.
Consequently, even over long timescales, the two-step pathway contributes less to generation of CP (\cref{figure:pathways}, right panels).
